outline!

### 2016-05-20 paper.tex
paper: related work mic drop
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

@@

\subsection{Physical Design}

@@

\paragraph*{Baseline Entry Storage Performance}
We begin the process of exploring the design space by exploiting the fact that
metadata management is a complexity and performance overhead that a full
implementation must incur beyond the costs of storing log entry data.
Therefore we first explore the design space by restricting the
space to log entry addressing and log entry storage (the \emph{I/O} action
shown in Figure~\ref{fig:corfu-sm}).  These two dimensions are
represented by the first two columns of Table~\ref{tab:pd-map} which describes
the entire design space. In the I/O column \emph{KV} corresponds to the
key-value interface, and the bytestream interface is represented by \emph{AP}
for an append strategy, and \emph{EX} for a strategy that writes to an
explicit bytestream offset (both described shortly).

@@

\paragraph*{Metadata Management}

@@

\paragraph*{Hardware and Software}

@@

@@

In this section we are going to be describing our way of creating interfaces.

@@

\section{Conclusion}

>>>>

%%% Anderson FAST 2016 IoT Time Series DB on Ceph

@@

\section{Physical Design}

@@

\subsection{Baseline Performance}

We begin the process of exploring the design space by exploiting the fact that
metadata management is a complexity and performance overhead that a full
implementation must incur beyond the costs of storing log entry data.
Therefore we first explore the design space by restricting the
space to log entry addressing and log entry storage (the \emph{I/O} action
shown in Figure~\ref{fig:corfu-sm}).  These two dimensions are
represented by the first two columns of Table~\ref{tab:pd-map} which describes
the entire design space. In the I/O column \emph{KV} corresponds to the
key-value interface, and the bytestream interface is represented by \emph{AP}
for an append strategy, and \emph{EX} for a strategy that writes to an
explicit bytestream offset (both described shortly).

@@

\subsection{Metadata Management}

@@

\subsection{Hardware and Software}

@@

\subsection{Optimization}

explain that the state space is large, this is hard for humans.
configuration, software versions, hardware versions, interface selections, and
future features.

@@

Describe big picture as if we are going to introduce something like bloom for
describing everything.

], Bloom is purely declarative: the syntax of a program contains the full
spec- ification of its semantics, and there is no need for the programmer to
understand or reason about the behavior of the evaluation engine. Bloom is
based on a formal temporal logic called Dedalu

We use a subset of bloom as a basis for defining interface.

Although we have not chosen to use the most powerful parts of the bloom (eg
task coordination and consistency)
language we have chosen to start with a powerful abstraction because we plan
to take this to 11 (see future work).

@@

{\bf Active storage.}
There is a wide variety of work related \emph{active storage} that seeks to
increase performance and reduce data movement by exploiting remote storage
resources. This concept has been applied in the context of on-disk
controllers and object-based storage
(T10)~\cite{riedel:vldb98,du:nwesp05,xie:msst11}.  Solutions to safety
concerns have examined using managed lanuages, sandbox technologies, as well
as restricting extension installation to
vendors~\cite{john:hiperio08,xie:msst11,runde:msst12}.

Techniques for remote storage processing have been applied in
application-specific domains for database and file system acceleration, as
well as in remote data filtering in cloud-based storage
environments~\cite{uysal:hpca00,chiu:iccs03,lim:msst08,gkantsidis:nsdi13}
Others have collected and used statistics to optimize the location of
computation in general workloads as well as database systems
~\cite{chen:cluster12,chen:icpp12,qiao:icde08}.

Most closely related to our work are efforts that consider specific
programming models in the context of active storage such as a stream-based
model~\cite{acharya:asplos98}, a model that assisted in optmiizing balancing
computation~\cite{wickremesinghe:hpdc022}, and optimization that took
advantage of read-only data to reorder operations~\cite{huston:fast04}.
While our goals are similar to previous work, we start with a declarative
language that will enable us to apply optimization techniques beyond
the limited domain-specific optimizations found in previous work.

\section{Conclusion and Future Work}

Include performance management topic in related work.
